A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
bib less space/conclusion

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefit from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. We also present a
 pseudo energy model taking into account the energetic contribution 
of the stacked base pairs and the isostericity of all base pairs.

By combining those two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 we are able  to efficiently 
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

>>>>

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefiting from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. We also showed a new
 pseudo energy model, taking into account the nearest-neighbour energy model 
and, to quantify geometrical differences,  the isostericity of all base pairs.

By combining those two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 into \texttt{RNApyro}, we show that we can
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.
